---
title: "Final Project"
author: "Shiloh Rivers"
date: "5/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(readxl)
library(tidyverse)
library(tidymodels)
library(ISLR)
library(lubridate)
library(rpart.plot)
library(vip)
library(janitor)
library(randomForest)
library(xgboost)
library(dplyr)
library(glue)
library(ISLR2)
library(discrim)
library(poissonreg)
library(corrr)
library(klaR)
library(corrplot)
library(glmnet)
library(parsnip)
library(tune)
library(modeldata)
library(workflows)
library(ranger)
library(vip)
library(kernlab)
library(vembedr)
tidymodels_prefer()
```


```{r}
embed_youtube("RQWejyx0gi8")
```
## Words

```{r}

codebook <- read_excel("archive/data (3) (1) (2).xlsx")
data <- read_excel("archive/data (3) (1) (2).xlsx", 2)

data <- as_tibble(data) %>% 
  clean_names()

```

standardize and normalize my data
remove engineTransmission_battery_cc_value_4

```{r}

# test_data <- data %>% 
#    mutate(inspectionDate = as.Date(inspectionStartTime)) %>% 
#    select(inspectionDate, everything(), -inspectionStartTime)

test_data <- data %>%
  mutate(appointment_num = row_number()) %>%
  select(appointment_num, everything(), -appointment_id)

test_data <- test_data %>%
  mutate(registration_date = as.Date(paste(year, month, "01", sep = "-"))) %>%
  select(appointment_num, inspection_start_time, registration_date, everything(), -year, -month)

test_data <- test_data %>% 
  mutate(engine_transmission_battery_value = as.factor(engine_transmission_battery_value))

levels(test_data$engine_transmission_battery_value)

test_data <- test_data %>%
  mutate(engine_transmission_battery_cc_value_0 = as.factor(engine_transmission_battery_cc_value_0))

levels(test_data$engine_transmission_battery_cc_value_0)

test_data <- test_data %>%
  mutate(engine_transmission_battery_cc_value_1 = as.factor(engine_transmission_battery_cc_value_1))

levels(test_data$engine_transmission_battery_cc_value_1)

test_data <- test_data %>%
  mutate(engine_transmission_battery_cc_value_2 = as.factor(engine_transmission_battery_cc_value_2))

levels(test_data$engine_transmission_battery_cc_value_2)

test_data <- test_data %>%
  mutate(engine_transmission_battery_cc_value_3 = as.factor(engine_transmission_battery_cc_value_3))

levels(test_data$engine_transmission_battery_cc_value_3)

test_data <- test_data %>%
  mutate(engine_transmission_battery_cc_value_4 = as.factor(engine_transmission_battery_cc_value_4))

levels(test_data$engine_transmission_battery_cc_value_4)

test_data <- test_data %>% 
  select(everything(), -engine_transmission_battery_cc_value_4)

test_data %>%
  filter(engine_transmission_battery_cc_value_0 == "Discharging light glowing")

test_data %>%
  filter(engine_transmission_battery_cc_value_1 == "Discharging light glowing")

test_data %>%
  filter(engine_transmission_battery_cc_value_2 == "Discharging light glowing")

test_data %>%
  filter(engine_transmission_battery_cc_value_3 == "Discharging light glowing")

test_data %>% 
  filter(engine_transmission_battery_value == "No")

```

Engine transmission battery value tells us if the battery is in good working condition or not. Each one of the following 4 variables (engine_transmission_battery_cc_value_0, engine_transmission_battery_cc_value_1, engine_transmission_battery_cc_value_2, engine_transmission_battery_cc_value_3, and engine_transmission_battery_cc_value_4) are each entries in a computer system. The mechanic fills in the first input and if he has some additional information he will continue to the second input, so on so forth. However, the same mechanic is not working everyday. Due to this confoundation, the information is not organized optimally. So I will instead create 5 yes/no factors "Changed", "Discharging light glowing", "Jump Start", "Not Working",and "Weak". Furthermore, the engine_transmission_battery_value yes/no factor is extraneous so it will be removed.

```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_battery_cc_value_0 == "Changed", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_battery_cc_value_1 == "Changed", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_battery_cc_value_2 == "Changed", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_battery_cc_value_3 == "Changed", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed_engine_transmission_battery = changed1 + changed2 + changed3 + changed4) %>% 
  mutate(changed_engine_transmission_battery = as.factor(changed_engine_transmission_battery)) %>% 
  select(appointment_num:registration_date, changed_engine_transmission_battery, everything(), -changed1, -changed2, -changed3, -changed4, -engine_transmission_battery_value)

levels(test_data$changed_engine_transmission_battery)

```


```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_battery_cc_value_0 == "Discharging light glowing", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_battery_cc_value_1 == "Discharging light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_battery_cc_value_2 == "Discharging light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_battery_cc_value_3 == "Discharging light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(discharging_light_glowing_engine_transmission_battery = changed1 + changed2 + changed3 + changed4) %>% 
  mutate(discharging_light_glowing_engine_transmission_battery = as.factor(discharging_light_glowing_engine_transmission_battery)) %>% 
  select(appointment_num:registration_date, discharging_light_glowing_engine_transmission_battery, everything(), -changed1, -changed2, -changed3, -changed4)

levels(test_data$discharging_light_glowing_engine_transmission_battery)

```


```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_battery_cc_value_0 == "Jump Start", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_battery_cc_value_1 == "Jump Start", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_battery_cc_value_2 == "Jump Start", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_battery_cc_value_3 == "Jump Start", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(jump_start_engine_transmission_battery = changed1 + changed2 + changed3 + changed4) %>% 
  mutate(jump_start_engine_transmission_battery = as.factor(jump_start_engine_transmission_battery)) %>% 
  select(appointment_num:registration_date, jump_start_engine_transmission_battery, everything(), -changed1, -changed2, -changed3, -changed4)

levels(test_data$jump_start_engine_transmission_battery)

```


```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_battery_cc_value_0 == "Not Working", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_battery_cc_value_1 == "Not Working", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_battery_cc_value_2 == "Not Working", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_battery_cc_value_3 == "Not Working", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(not_working_engine_transmission_battery = changed1 + changed2 + changed3 + changed4) %>% 
  mutate(not_working_engine_transmission_battery = as.factor(not_working_engine_transmission_battery)) %>% 
  select(appointment_num:registration_date, not_working_engine_transmission_battery, everything(), -changed1, -changed2, -changed3, -changed4)

levels(test_data$not_working_engine_transmission_battery)

```


```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_battery_cc_value_0 == "Weak", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_battery_cc_value_1 == "Weak", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_battery_cc_value_2 == "Weak", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_battery_cc_value_3 == "Weak", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(weak_engine_transmission_battery = changed1 + changed2 + changed3 + changed4) %>% 
  mutate(weak_engine_transmission_battery = as.factor(weak_engine_transmission_battery)) %>% 
  select(appointment_num:registration_date, weak_engine_transmission_battery, everything(), -changed1, -changed2, -changed3, -changed4, -engine_transmission_battery_cc_value_0, -engine_transmission_battery_cc_value_1, -engine_transmission_battery_cc_value_2, -engine_transmission_battery_cc_value_3)

levels(test_data$weak_engine_transmission_battery)

```


```{r}
levels(as.factor(test_data$engine_transmission_engine_oil_level_dipstick_cc_value_0))

test_data <- test_data %>% 
  mutate(broken_engine_transmission_engine_oil_level_dipstick = if_else(engine_transmission_engine_oil_level_dipstick_cc_value_0 == "Broken", 1, 0, 0)) %>%
  mutate(broken_engine_transmission_engine_oil_level_dipstick = as.factor(broken_engine_transmission_engine_oil_level_dipstick)) %>% 
  select(appointment_num:changed_engine_transmission_battery, broken_engine_transmission_engine_oil_level_dipstick, everything(), -engine_transmission_engineoil_level_dipstick_value, -engine_transmission_engine_oil_level_dipstick_cc_value_0)

levels(test_data$broken_engine_transmission_engine_oil_level_dipstick)
```


```{r}

levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_0))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_1))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_2))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_3))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_4))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_5))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_6))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_7))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_8))
levels(as.factor(test_data$engine_transmission_engine_oil_cc_value_9))
```

```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Dirty", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Dirty", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Dirty", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Dirty", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Dirty", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Dirty", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Dirty", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(dirty_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(dirty_engine_transmission_engine_oil = as.factor(dirty_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, dirty_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

levels(test_data$dirty_engine_transmission_engine_oil)

```


```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Leakage from Side cover", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Leakage from Side cover", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Leakage from Side cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Leakage from Side cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Leakage from Side cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Leakage from Side cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Leakage from Side cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(leakage_from_side_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(leakage_from_side_engine_transmission_engine_oil = as.factor(leakage_from_side_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, leakage_from_side_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

levels(test_data$leakage_from_side_engine_transmission_engine_oil)

```


```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Leakage from Sump/chamber", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Leakage from Sump/chamber", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Leakage from Sump/chamber", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Leakage from Sump/chamber", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Leakage from Sump/chamber", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Leakage from Sump/chamber", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Leakage from Sump/chamber", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(leakage_from_sump_chamber_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(leakage_from_sump_chamber_engine_transmission_engine_oil = as.factor(leakage_from_sump_chamber_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, leakage_from_sump_chamber_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

levels(test_data$leakage_from_sump_chamber_engine_transmission_engine_oil)

```

```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Leakage from Tappet Cover", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Leakage from Tappet Cover", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Leakage from Tappet Cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Leakage from Tappet Cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Leakage from Tappet Cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Leakage from Tappet Cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Leakage from Tappet Cover", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(leakage_from_tappet_cover_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(leakage_from_tappet_cover_engine_transmission_engine_oil = as.factor(leakage_from_tappet_cover_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, leakage_from_tappet_cover_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

levels(test_data$leakage_from_tappet_cover_engine_transmission_engine_oil)

```

```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Leaking", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Leaking", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Leaking", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Leaking", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Leaking", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Leaking", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Leaking", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(leaking_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(leaking_engine_transmission_engine_oil = as.factor(leaking_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, leaking_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

levels(test_data$leaking_engine_transmission_engine_oil)

```


```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Leakage from Turbo Charger", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Leakage from Turbo Charger", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Leakage from Turbo Charger", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Leakage from Turbo Charger", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Leakage from Turbo Charger", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Leakage from Turbo Charger", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Leakage from Turbo Charger", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(leakage_from_turbo_charger_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(leakage_from_turbo_charger_engine_transmission_engine_oil = as.factor(leakage_from_turbo_charger_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, leakage_from_turbo_charger_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

levels(test_data$leakage_from_turbo_charger_engine_transmission_engine_oil)

```


```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Mixed with Coolant", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Mixed with Coolant", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Mixed with Coolant", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Mixed with Coolant", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Mixed with Coolant", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Mixed with Coolant", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Mixed with Coolant", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(mixed_with_coolant_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(mixed_with_coolant_engine_transmission_engine_oil = as.factor(mixed_with_coolant_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, mixed_with_coolant_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

levels(test_data$mixed_with_coolant_engine_transmission_engine_oil)

```



```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Low Pressure warning light glowing", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Low Pressure warning light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Low Pressure warning light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Low Pressure warning light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Low Pressure warning light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Low Pressure warning light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Low Pressure warning light glowing", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(low_pressure_warning_light_glowing_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(low_pressure_warning_light_glowing_engine_transmission_engine_oil = as.factor(low_pressure_warning_light_glowing_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, low_pressure_warning_light_glowing_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

levels(test_data$low_pressure_warning_light_glowing_engine_transmission_engine_oil)

```



```{r}

test_data <- test_data %>% 
  mutate(changed1 = if_else(engine_transmission_engine_oil_cc_value_0 == "Level Low", 1, 0, 0)) %>%
  select(changed1, everything())

test_data <- test_data %>% 
  mutate(changed2 = if_else(engine_transmission_engine_oil_cc_value_1 == "Level Low", 1, 0, 0)) %>%
  select(changed1, changed2, everything())

test_data <- test_data %>% 
  mutate(changed3 = if_else(engine_transmission_engine_oil_cc_value_2 == "Level Low", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, everything())

test_data <- test_data %>% 
  mutate(changed4 = if_else(engine_transmission_engine_oil_cc_value_3 == "Level Low", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed5 = if_else(engine_transmission_engine_oil_cc_value_4 == "Level Low", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed6 = if_else(engine_transmission_engine_oil_cc_value_5 == "Level Low", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(changed7 = if_else(engine_transmission_engine_oil_cc_value_6 == "Level Low", 1, 0, 0)) %>%
  select(changed1, changed2, changed3, changed4, everything())

test_data <- test_data %>% 
  mutate(level_low_engine_transmission_engine_oil = changed1 + changed2 + changed3 + changed4 + changed5 + changed6 + changed7) %>% 
  mutate(level_low_engine_transmission_engine_oil = as.factor(level_low_engine_transmission_engine_oil)) %>% 
  select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, level_low_engine_transmission_engine_oil, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)

test_data <- test_data %>% 
  select(everything(), -engine_transmission_engine_oil, -engine_transmission_engine_oil_cc_value_0, -engine_transmission_engine_oil_cc_value_1, -engine_transmission_engine_oil_cc_value_2, -engine_transmission_engine_oil_cc_value_3, -engine_transmission_engine_oil_cc_value_4, -engine_transmission_engine_oil_cc_value_5, -engine_transmission_engine_oil_cc_value_6, -engine_transmission_engine_oil_cc_value_7, -engine_transmission_engine_oil_cc_value_8, -engine_transmission_engine_oil_cc_value_9)

levels(test_data$level_low_engine_transmission_engine_oil)

```


```{r}

levels(as.factor(test_data$engine_transmission_engine_cc_value_0))
levels(as.factor(test_data$engine_transmission_engine_cc_value_1))
levels(as.factor(test_data$engine_transmission_engine_cc_value_2))
levels(as.factor(test_data$engine_transmission_engine_cc_value_3))
levels(as.factor(test_data$engine_transmission_engine_cc_value_4))
levels(as.factor(test_data$engine_transmission_engine_cc_value_5))
levels(as.factor(test_data$engine_transmission_engine_cc_value_6))
levels(as.factor(test_data$engine_transmission_engine_cc_value_7))
levels(as.factor(test_data$engine_transmission_engine_cc_value_8))
levels(as.factor(test_data$engine_transmission_engine_cc_value_9))
```


```{r}
# test_data$paste("var","name", sep = "_")
# for (n in length(levels)){
# for (m in length(variables)){
# test_data <- test_data %>% 
#   mutate(var_name = if_else(variables[m] == levels[n], 1, 0, 0)) %>% 
#   select(var_name, everything())
# }}
# 
# 
# minimizer <- function(levels, variables) {
#   
# for (n in length(levels)){
# for (m in length(variables)){
#   var_name = paste("changed", m, sep = "")
# test_data <- test_data %>% 
#   mutate(var_name = if_else(variables[m] == levels[n], 1, 0, 0))
# 
# new_variable_name = paste(levels[n], variables[m], sep = "_")
# 
# print(new_variable_name)
# test_data <- test_data %>% 
#   mutate(new_variable_name = 0)
# 
# test_data <- test_data %>% 
#   mutate(new_variable_name = new_variable_name + var_name) %>% 
#   select(everything())
# 
# }}
# }
# 
# levels <- c("Car not working on Petrol", "Fuel Leakage From Injector", "MIL light glowing", "Misfiring", "Not converting to CNG", "Over heating", "Repaired", "RPM fluctuating", "RPM not increasing", "Seized", "Sump Damaged", "Turbo charger not working")
# 

# 
# minimizer(levels,variables)
# 
# for (n in length(levels)){
#   print(paste(levels[n], variables[n]))
# }
# 
# select(appointment_num:broken_engine_transmission_engine_oil_level_dipstick, new_variable_name, everything(), -changed1, -changed2, -changed3, -changed4, -changed5, -changed6, -changed7)
# mutate(new_variable_name = as.factor(new_variable_name)) %>% 
# 
# levels(test_data$new_variable_name)

```

```{r}
# for (i in 1:5) {
#   assign(paste("t",files[i],sep=""), read.tucson(files[i],header=NULL))
# }
# 
# assign(paste("t",1, sep = ""), as.list(data$appointment_id))
# 
# for(i in test_data)){
#   name <- paste("t", i, sep = "_")
#   assign(name,  transpose(df_before_transpose[[i]]))
# }
# 
# m = 1
# paste("what", 1, sep = "") = c(1,2)
# shazbot <- data.frame(assign(paste("orca", m, sep = ""), data$appointment_id), assign(paste("orca", m, sep = ""), data$inspection_start_time))
# 
# shazbot <- as.tibble(shazbot)
# 
# get(paste("orca", 1, sep = ""))
# rm(orca1)
# 
# test_data <- test_data %>% 
#    transmute(assign(paste("changed", 1, sep = "")))
# test_data %>% 
#   select(assign(paste("changed", 1, sep = ""))
  
  
# minimizer <- function(levels, variables) {
#   
# for (n in length(levels)){
# for (m in length(variables)){
#   assign(paste("changed", m, sep = ""), )
# test_data <- test_data %>% 
#   assign(paste("changed", m, sep = ""), 0)
#   mutate(var_name = if_else(variables[m] == levels[n], 1, 0, 0))
# 
# new_variable_name = paste(levels[n], variables[m], sep = "_")
# 
# print(new_variable_name)
# test_data <- test_data %>% 
#   mutate(new_variable_name = 0)
# 
# test_data <- test_data %>% 
#   mutate(new_variable_name = new_variable_name + var_name) %>% 
#   select(everything())
# 
# }}
# }

# install.packages("lazyeval")
# library(lazyeval)
# from <- "appointment_num"
# 
# 
# data %>%
#   mutate(diff=interp(~from, from=as.name(from)))
# 
# !!as.name(paste("appointment", "num", sep = "_"))
# 
# test_data %>%
#   mutate((!!as.name(paste("changed", 1, sep = ""))) = 0) %>% 
#   select((!!as.name(paste("changed", 1, sep = ""))))
# 
# minimizer <- function(levels, variables) {
# 
# for (n in length(levels)){
# for (m in length(variables)){
#   
# test_data <- test_data %>%
#   mutate(as.name(paste("changed", m, sep = "")) = if_else(variables[m] == levels[n], 1, 0, 0))
# 
# new_variable_name = paste(levels[n], variables[m], sep = "_")
# 
# print(new_variable_name)
# test_data <- test_data %>%
#   mutate(new_variable_name = 0)
# 
# test_data <- test_data %>%
#   mutate(new_variable_name = new_variable_name + var_name) %>%
#   select(everything())
# 
# }}
# }


```
```{r}
# 
# 
# 
# multipetal <- function(df, n) {
#   mutate(df, "petal.{n}" := Petal.Width * n)
# }
# 
# meanofcol <- function(df, col) {
#   mutate(df, "Mean of {{col}}" := mean({{col}}))
# }
# 
# meanofcol(iris, Petal.Width)
# 
# minimizer <- function(levels, variables) {
# 
# for (n in length(levels)){
# for (m in length(variables)){
# 
# test_data <- test_data %>%
#   mutate(as.name(paste("changed", m, sep = "")) = if_else(variables[m] == levels[n], 1, 0, 0))
# 
# new_variable_name = paste(levels[n], variables[m], sep = "_")
# 
# print(new_variable_name)
# test_data <- test_data %>%
#   mutate(new_variable_name = 0)
# 
# test_data <- test_data %>%
#   mutate(new_variable_name = new_variable_name + var_name) %>%
#   select(everything())
# 
# }}
# }

```

```{r}

multichange <- function(df, z, w) {
  x = variables[z]
  y = levels[w]
  mutate(df, "change{z}" := 1)
  mutate(df, "change{z}" := if_else(.data[[x]] == y, 1, 0, 0))
}

variables <- c("engine_transmission_engine_cc_value_0", "engine_transmission_engine_cc_value_1", "engine_transmission_engine_cc_value_2", "engine_transmission_engine_cc_value_3", "engine_transmission_engine_cc_value_4", "engine_transmission_engine_cc_value_5", "engine_transmission_engine_cc_value_6", "engine_transmission_engine_cc_value_7", "engine_transmission_engine_cc_value_8", "engine_transmission_engine_cc_value_9", "engine_transmission_engine_cc_value_10")

levels <- c("Car not working on Petrol", "Fuel Leakage From Injector", "MIL light glowing", "Misfiring", "Not converting to CNG", "Over heating", "Repaired", "RPM fluctuating", "RPM not increasing", "Seized", "Sump Damaged", "Turbo charger not working")







# n = c(1:11)
# for(i in n){
#   test_data <- multichange(test_data, i)
# }

# n = c(1:11)
# m = c(1:12)
#m = 4
for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_engine" := change1 + change2 + change3 + change4 + change5 + change6 + change7 + change8 + change9 + change10 + change11)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -change2, -change3, -change4, -change5, -change6, -change7, -change8, -change9, -change10, -change11, -engine_transmission_engine_cc_value_0, -engine_transmission_engine_cc_value_1, -engine_transmission_engine_cc_value_2, -engine_transmission_engine_cc_value_3, -engine_transmission_engine_cc_value_4, -engine_transmission_engine_cc_value_5, -engine_transmission_engine_cc_value_6, -engine_transmission_engine_cc_value_7, -engine_transmission_engine_cc_value_8, -engine_transmission_engine_cc_value_9, -engine_transmission_engine_cc_value_10, -engine_transmission_engine_value)

test_data <- test_data %>% 
  mutate(car_not_working_on_petrol_engine_transmission_engine = as.factor(car_not_working_on_petrol_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(fuel_leakage_from_injector_engine_transmission_engine = as.factor(fuel_leakage_from_injector_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(mil_light_glowing_engine_transmission_engine = as.factor(mil_light_glowing_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(misfiring_engine_transmission_engine = as.factor(misfiring_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(not_converting_to_cng_engine_transmission_engine = as.factor(not_converting_to_cng_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(over_heating_engine_transmission_engine = as.factor(over_heating_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(repaired_engine_transmission_engine = as.factor(repaired_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(rpm_fluctuating_engine_transmission_engine = as.factor(rpm_fluctuating_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(rpm_not_increasing_engine_transmission_engine = as.factor(rpm_not_increasing_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(seized_engine_transmission_engine = as.factor(seized_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(sump_damaged_engine_transmission_engine = as.factor(sump_damaged_engine_transmission_engine))

test_data <- test_data %>% 
  mutate(turbo_charger_not_working_engine_transmission_engine = as.factor(turbo_charger_not_working_engine_transmission_engine))




# minimizer <- function(levels, variables) {
# 
# for (n in length(levels)){
# for (m in length(variables)){
#   
# test_data <- test_data %>%
#   mutate(as.name(paste("changed", m, sep = "")) = if_else(variables[m] == levels[n], 1, 0, 0))
# 
# new_variable_name = paste(levels[n], variables[m], sep = "_")
# 
# print(new_variable_name)
# test_data <- test_data %>%
#   mutate(new_variable_name = 0)
# 
# test_data <- test_data %>%
#   mutate(new_variable_name = new_variable_name + var_name) %>%
#   select(everything())
# 
# }}
```

```{r}

levels(as.factor(test_data$engine_transmission_coolant_cc_value_0))

variables <- c("engine_transmission_coolant_cc_value_0", "engine_transmission_coolant_cc_value_1", "engine_transmission_coolant_cc_value_2", "engine_transmission_coolant_cc_value_3")

levels <- c("Dirty", "Leaking", "Mixed with Engine Oil", "Radiator Damaged")

for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_coolant" := change1 + change2 + change3 + change4)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -change2, -change3, -change4, -engine_transmission_coolant_cc_value_0, -engine_transmission_coolant_cc_value_1, -engine_transmission_coolant_cc_value_2, -engine_transmission_coolant_cc_value_3, -engine_transmission_coolant_value)

test_data <- test_data %>% 
  mutate(dirty_engine_transmission_coolant = as.factor(dirty_engine_transmission_coolant))

test_data <- test_data %>% 
  mutate(leaking_engine_transmission_coolant = as.factor(leaking_engine_transmission_coolant))

test_data <- test_data %>% 
  mutate(mixed_with_engine_oil_engine_transmission_coolant = as.factor(mixed_with_coolant_engine_transmission_engine_oil))

test_data <- test_data %>% 
  mutate(radiator_damaged_engine_transmission_coolant = as.factor(radiator_damaged_engine_transmission_coolant))

```

```{r}

levels(as.factor(test_data$engine_transmission_engine_mounting_cc_value_0))

variables <- c("engine_transmission_engine_mounting_cc_value_0")

levels <- c("Broken", "Excess Vibration", "Loose")

for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_engine_mounting" := change1)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -engine_transmission_engine_mounting_cc_value_0, -engine_transmission_engine_mounting_value)

test_data <- test_data %>% 
  mutate(broken_engine_transmission_engine_mounting = as.factor(broken_engine_transmission_engine_mounting))

test_data <- test_data %>% 
  mutate(excess_vibration_engine_transmission_engine_mounting = as.factor(excess_vibration_engine_transmission_engine_mounting))

test_data <- test_data %>% 
  mutate(loose_engine_transmission_engine_mounting = as.factor(loose_engine_transmission_engine_mounting))

```


```{r}

levels(as.factor(test_data$engine_transmission_engine_sound_cc_value_0))

variables <- c("engine_transmission_engine_sound_cc_value_0", "engine_transmission_engine_sound_cc_value_1", "engine_transmission_engine_sound_cc_value_2", "engine_transmission_engine_sound_cc_value_3", "engine_transmission_engine_sound_cc_value_4", "engine_transmission_engine_sound_cc_value_5")

levels <- c("Alternator Brg Noise", "Engine Auxiliary Noise", "Injector Noise", "Tappet Noise", "Timing Noise", "Water Pump Brg Noise", "Whistling Noise-Turbo")

for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_engine_sound" := change1 + change2 + change3 + change4 + change5 + change6)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -change2, -change3, -change4, -change5, -change6, -engine_transmission_engine_sound_cc_value_0, -engine_transmission_engine_sound_cc_value_1, -engine_transmission_engine_sound_cc_value_2, -engine_transmission_engine_sound_cc_value_3, -engine_transmission_engine_sound_cc_value_4, -engine_transmission_engine_sound_cc_value_5,  -engine_transmission_engine_sound_value)

test_data <- test_data %>% 
  mutate(alternator_brg_noise_engine_transmission_engine_sound = as.factor(alternator_brg_noise_engine_transmission_engine_sound))

test_data <- test_data %>% 
  mutate(engine_auxiliary_noise_engine_transmission_engine_sound = as.factor(engine_auxiliary_noise_engine_transmission_engine_sound))

test_data <- test_data %>% 
  mutate(injector_noise_engine_transmission_engine_sound = as.factor(injector_noise_engine_transmission_engine_sound))

test_data <- test_data %>% 
  mutate(tappet_noise_engine_transmission_engine_sound = as.factor(tappet_noise_engine_transmission_engine_sound))

test_data <- test_data %>% 
  mutate(timing_noise_engine_transmission_engine_sound = as.factor(timing_noise_engine_transmission_engine_sound))

test_data <- test_data %>% 
  mutate(water_pump_brg_noise_engine_transmission_engine_sound = as.factor(water_pump_brg_noise_engine_transmission_engine_sound))

test_data <- test_data %>% 
  mutate(whistling_noise_turbo_engine_transmission_engine_sound = as.factor(whistling_noise_turbo_engine_transmission_engine_sound))


```


```{r}

test_data_copy <- test_data

levels(as.factor(test_data$engine_transmission_exhaust_smoke_cc_value_0))

variables <- c("engine_transmission_exhaust_smoke_cc_value_0")

levels <- c("Black", "Blue", "Leakage from manifold", "Noise from silencer assembly", "Silencer assembly damaged", "White")

for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_exhaust_smoke" := change1)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -engine_transmission_exhaust_smoke_cc_value_0, -engine_transmission_exhaust_smoke_value)

test_data <- test_data %>% 
  mutate(black_engine_transmission_exhaust_smoke = as.factor(black_engine_transmission_exhaust_smoke))

test_data <- test_data %>% 
  mutate(blue_engine_transmission_exhaust_smoke = as.factor(blue_engine_transmission_exhaust_smoke))

test_data <- test_data %>% 
  mutate(leakage_from_manifold_engine_transmission_exhaust_smoke = as.factor(leakage_from_manifold_engine_transmission_exhaust_smoke))

test_data <- test_data %>% 
  mutate(noise_from_silencer_assembly_engine_transmission_exhaust_smoke = as.factor(noise_from_silencer_assembly_engine_transmission_exhaust_smoke))

test_data <- test_data %>% 
  mutate(silencer_assembly_damaged_engine_transmission_exhaust_smoke = as.factor(silencer_assembly_damaged_engine_transmission_exhaust_smoke))

test_data <- test_data %>% 
  mutate(white_engine_transmission_exhaust_smoke = as.factor(white_engine_transmission_exhaust_smoke))

```

```{r}

test_data_copy <- test_data

levels(as.factor(test_data_copy$engine_transmission_engine_blow_by_back_compression_cc_value_0))

variables <- c("engine_transmission_engine_blow_by_back_compression_cc_value_0")

levels <- c("Back Compression Exist", "NO Blow-by", "Oil spillage on Idle", "Perm. blow by & oil spillage on idle", "Perm. Blow By on idle")

for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_engine_blow_by_back_compression" := change1)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -engine_transmission_engine_blow_by_back_compression_cc_value_0, -engine_transmission_engine_blow_by_back_compression_value)

test_data <- test_data %>% 
  mutate(back_compression_exist_engine_transmission_engine_blow_by_back_compression = as.factor(back_compression_exist_engine_transmission_engine_blow_by_back_compression))

test_data <- test_data %>% 
  mutate(no_blow_by_engine_transmission_engine_blow_by_back_compression = as.factor(no_blow_by_engine_transmission_engine_blow_by_back_compression))

test_data <- test_data %>% 
  mutate(oil_spillage_on_idle_engine_transmission_engine_blow_by_back_compression = as.factor(oil_spillage_on_idle_engine_transmission_engine_blow_by_back_compression))

test_data <- test_data %>% 
  mutate(perm_blow_by_oil_spillage_on_idle_engine_transmission_engine_blow_by_back_compression = as.factor(perm_blow_by_oil_spillage_on_idle_engine_transmission_engine_blow_by_back_compression))

test_data <- test_data %>% 
  mutate(perm_blow_by_on_idle_engine_transmission_engine_blow_by_back_compression = as.factor(perm_blow_by_on_idle_engine_transmission_engine_blow_by_back_compression))

```

```{r}

test_data_copy <- test_data

levels(as.factor(test_data_copy$engine_transmission_clutch_cc_value_0))

variables <- c("engine_transmission_clutch_cc_value_0", "engine_transmission_clutch_cc_value_1", "engine_transmission_clutch_cc_value_2", "engine_transmission_clutch_cc_value_3", "engine_transmission_clutch_cc_value_4", "engine_transmission_clutch_cc_value_5", "engine_transmission_clutch_cc_value_6")

levels <- c("Auto Transmission Not Satisfactory", "Bearing Noise", "Burning", "Hard", "Low Pick Up", "Slip", "Spongy")

for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_clutch" := change1 + change2 + change3 + change4 + change5 + change6 + change7)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -change2, -change3, -change4, -change5, -change6, -change7, -engine_transmission_clutch_cc_value_0, -engine_transmission_clutch_cc_value_1, -engine_transmission_clutch_cc_value_2, -engine_transmission_clutch_cc_value_3, -engine_transmission_clutch_cc_value_4, -engine_transmission_clutch_cc_value_5, -engine_transmission_clutch_cc_value_6, -engine_transmission_clutch_value)

test_data <- test_data %>% 
  mutate(auto_transmission_not_satisfactory_engine_transmission_clutch = as.factor(auto_transmission_not_satisfactory_engine_transmission_clutch))

test_data <- test_data %>% 
  mutate(bearing_noise_engine_transmission_clutch = as.factor(bearing_noise_engine_transmission_clutch))

test_data <- test_data %>% 
  mutate(burning_engine_transmission_clutch = as.factor(burning_engine_transmission_clutch))

test_data <- test_data %>% 
  mutate(hard_engine_transmission_clutch = as.factor(hard_engine_transmission_clutch))

test_data <- test_data %>% 
  mutate(low_pick_up_engine_transmission_clutch = as.factor(low_pick_up_engine_transmission_clutch))

test_data <- test_data %>% 
  mutate(slip_engine_transmission_clutch = as.factor(slip_engine_transmission_clutch))

test_data <- test_data %>% 
  mutate(spongy_engine_transmission_clutch = as.factor(spongy_engine_transmission_clutch))

```

```{r}

test_data_copy <- test_data

levels(as.factor(test_data_copy$engine_transmission_gear_shifting_cc_value_0))

variables <- c("engine_transmission_gear_shifting_cc_value_0", "engine_transmission_gear_shifting_cc_value_1", "engine_transmission_gear_shifting_cc_value_2")

levels <- c("Abnormal Noise", "Automatic Transmission not working properly", "Hard", "Not Engaging")

for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_gear_shifting" := change1 + change2 + change3)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -change2, -change3, -engine_transmission_gear_shifting_cc_value_0, -engine_transmission_gear_shifting_cc_value_1, -engine_transmission_gear_shifting_cc_value_2, -engine_transmission_gear_shifting_value)

test_data <- test_data %>% 
  mutate(abnormal_noise_engine_transmission_gear_shifting = as.factor(abnormal_noise_engine_transmission_gear_shifting))

test_data <- test_data %>% 
  mutate(automatic_transmission_not_working_properly_engine_transmission_gear_shifting = as.factor(automatic_transmission_not_working_properly_engine_transmission_gear_shifting))

test_data <- test_data %>% 
  mutate(hard_engine_transmission_gear_shifting = as.factor(hard_engine_transmission_gear_shifting))

test_data <- test_data %>% 
  mutate(not_engaging_engine_transmission_gear_shifting = as.factor(not_engaging_engine_transmission_gear_shifting))

```

```{r}

test_data_copy <- test_data

levels(as.factor(test_data_copy$engine_transmission_comments_value_0))
# levels(as.factor(test_data_copy$engine_transmission_comments_value_1))
# levels(as.factor(test_data_copy$engine_transmission_comments_value_2))
# levels(as.factor(test_data_copy$engine_transmission_comments_value_3))
# levels(as.factor(test_data_copy$engine_transmission_comments_value_4))

variables <- c("engine_transmission_comments_value_0", "engine_transmission_comments_value_1", "engine_transmission_comments_value_2", "engine_transmission_comments_value_3", "engine_transmission_comments_value_4")

levels <- c("4WD / AWD not working", "Car not in running condition, towing required", "Electrical wiring Damaged", "Pickup Low", "Radiator Fan not working", "Starter Motor / Solenoid malfunctioning")

for(r in c(1:length(levels))){
  for(i in c(1:length(variables))){
    test_data <- multichange(test_data, i, r)
  }
    level_name = levels[r]
    test_data <- test_data %>% 
      mutate("{level_name}_engine_transmission_comments" := change1 + change2 + change3 + change4 + change5)
}

test_data <- test_data %>% 
  clean_names()

test_data <- test_data %>%
    select(everything(), -change1, -change2, -change3, -change4, -change5, -engine_transmission_comments_value_0, -engine_transmission_comments_value_1, -engine_transmission_comments_value_2, -engine_transmission_comments_value_3, -engine_transmission_comments_value_4)

test_data <- test_data %>% 
  mutate(x4wd_awd_not_working_engine_transmission_comments = as.factor(x4wd_awd_not_working_engine_transmission_comments))

test_data <- test_data %>% 
  mutate(car_not_in_running_condition_towing_required_engine_transmission_comments = as.factor(car_not_in_running_condition_towing_required_engine_transmission_comments))

test_data <- test_data %>% 
  mutate(electrical_wiring_damaged_engine_transmission_comments = as.factor(electrical_wiring_damaged_engine_transmission_comments))

test_data <- test_data %>% 
  mutate(pickup_low_engine_transmission_comments = as.factor(pickup_low_engine_transmission_comments))

test_data <- test_data %>% 
  mutate(radiator_fan_not_working_engine_transmission_comments = as.factor(radiator_fan_not_working_engine_transmission_comments))

test_data <- test_data %>% 
  mutate(starter_motor_solenoid_malfunctioning_engine_transmission_comments = as.factor(starter_motor_solenoid_malfunctioning_engine_transmission_comments))

```

```{r}

test_data_copy <- test_data

levels(as.factor(test_data_copy$fuel_type))

test_data <- test_data %>% 
  mutate(fuel_type = as.factor(fuel_type))

```

```{r}

set.seed(3435)
data_split <- initial_split(test_data, strata = "rating_engine_transmission")

data_train <- training(data_split)
data_test <- testing(data_split)

data_folds <- vfold_cv(data_train, v = 5, strata = "rating_engine_transmission")

hist(data$rating_engine_transmission)
```

```{r}

recipe <- recipe(rating_engine_transmission ~ ., data = data_train) %>%
  step_dummy(all_nominal_predictors()) %>% 
  step_center(all_nominal_predictors()) %>% 
  step_scale(all_nominal_predictors())

# recipe_class <- recipe(rating_engine_transmission ~ ., data = data_train) %>%
#   step_dummy(all_nominal_predictors()) %>% 
#   step_center(all_nominal_predictors()) %>% 
#   step_scale(all_nominal_predictors()) %>% 
#   step_num2factor(rating_engine_transmission, levels = c("0.5","1.0","1.5","2.0","2.5","3.0","3.5","4.0","4.5","5.0"))

lm_model <- linear_reg() %>% 
  set_engine("lm")

lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(recipe)

lm_fit <- fit(lm_wflow, data_train)


train_res <- predict(lm_fit, new_data = data_train)
train_res <- bind_cols(train_res, data_train %>% select(rating_engine_transmission))

metrics <- metric_set(rmse, rsq, mae)
metrics(train_res, truth = rating_engine_transmission, 
                estimate = .pred)

augment(lm_fit, new_data = data_test) %>%
  ggplot(aes(rating_engine_transmission, .pred)) +
  geom_point(alpha = 0.5)

```

Roughly 43% of the variation in engine transmission rating is explained by this linear model.

```{r}

data_train %>% 
  ggplot(aes(x = weak_engine_transmission_battery)) +
  geom_bar()

table <- data_train %>% 
  group_by(weak_engine_transmission_battery) %>% 
  summarise(count = n())

table[2,2]/table[1,2]

data_train %>% 
  ggplot(aes(x = broken_engine_transmission_engine_oil_level_dipstick)) +
  geom_bar()

table <- data_train %>% 
  group_by(broken_engine_transmission_engine_oil_level_dipstick) %>% 
  summarise(count = n())

table[2,2]/table[1,2]

data_train %>% 
  ggplot(aes(x = sump_damaged_engine_transmission_engine)) +
  geom_bar()

table <- data_train %>% 
  group_by(sump_damaged_engine_transmission_engine) %>% 
  summarise(count = n())

table[2,2]/table[1,2]

```

```{r}

cor_data_train <- data_train %>%
  select(is.numeric) %>%
  correlate(use="complete.obs")

rplot(cor_data_train)

```

```{r}

data_train %>% 
  group_by(rating_engine_transmission) %>% 
  summarise(count = n())



```


```{r}

# log_reg <- logistic_reg() %>% 
#   set_engine("glm") %>% 
#   set_mode("classification")
# 
# log_wkflow <- workflow() %>% 
#   add_model(log_reg) %>% 
#   add_recipe(recipe)
# 
# log_fit <- fit(log_wkflow, data_train)

```



```{r}

tree_spec <- decision_tree() %>%
  set_engine("rpart")

class_tree_spec <- tree_spec %>%
  set_mode("regression")

class_tree_wf <- workflow() %>%
  add_model(class_tree_spec %>% set_args(cost_complexity = tune())) %>%
  add_recipe(recipe)

param_grid <- grid_regular(cost_complexity(range = c(-5, -1)), levels = 10)

# tune_res1 <- tune_grid(
#   class_tree_wf, 
#   resamples = data_folds, 
#   grid = param_grid, 
#   metrics = metric_set(rmse, rsq, mae)
# )

#save(tune_res1, file = "tune_res1.rda")
load(file = "tune_res1.rda")

autoplot(tune_res1)


head(filter(arrange(collect_metrics(tune_res1), mean), .metric == "mae"))

head(filter(arrange(collect_metrics(tune_res1), mean), .metric == "rmse"))

head(filter(arrange(collect_metrics(tune_res1), desc(mean)), .metric == "rsq"))


best_complexity <- select_best(tune_res1)

class_tree_final <- finalize_workflow(class_tree_wf, best_complexity)

class_tree_final_fit <- fit(class_tree_final, data = data_train)

class_tree_final_fit %>%
  extract_fit_engine() %>%
  rpart.plot()

augment(class_tree_final_fit, new_data = data_test) %>%
  ggplot(aes(rating_engine_transmission, .pred)) +
  geom_point(alpha = 0.5)

augment(class_tree_final_fit, new_data = data_test) %>%
  rmse(truth = rating_engine_transmission, estimate = .pred)
```
```{r}

reg_rf_spec <- rand_forest() %>%
  set_engine(engine = "ranger", importance = "impurity") %>%
  set_mode("regression")

reg_rf_wf <- workflow() %>%
  add_model(reg_rf_spec %>% set_args(mtry = 8, trees = 1000, min_n = 100)) %>%
  add_recipe(recipe)

param_grid <- grid_regular(mtry(range = c(7, 9)), trees(range = c(250,2000)), min_n(range = c(10,300)), levels = 5)

# tune_res2 <- tune_grid(
#    class_rf_wf,
#    resamples = data_folds,
#    grid = param_grid,
#    metrics = metric_set(rmse, rsq, mae)
# )

# save(tune_res2, file = "data/tune_res2.rda")
# load(file = "data/tune_res2.rda")
# 
# autoplot(tune_res2)

#class_rf_final <- finalize_workflow(class_rf_wf, best_complexity)

#reg_rf__fit <- fit(reg_rf_wf, data = data_train)

#save(reg_rf__fit, file = "reg_rf__fit.rda")
load(file = "reg_rf__fit.rda")

reg_rf__fit %>%
  pull_workflow_fit()%>%
  vip()

augment(reg_rf__fit, new_data = data_test) %>%
  ggplot(aes(rating_engine_transmission, .pred)) +
  geom_point(alpha = 0.5)

augment(reg_rf__fit, new_data = data_test) %>%
  rmse(truth = rating_engine_transmission, estimate = .pred)
```

```{r}

reg_rf_spec <- boost_tree() %>%
  set_engine(engine = "xgboost") %>%
  set_mode("regression")

recipe2 <- recipe(rating_engine_transmission ~ ., data = data_train) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_center(all_nominal_predictors()) %>%
  step_scale(all_nominal_predictors()) %>%
  step_rm(inspection_start_time, registration_date)

reg_rf_wf <- workflow() %>%
  add_model(reg_rf_spec %>% set_args(trees = 1000)) %>%
  add_recipe(recipe2)

param_grid <- grid_regular(trees(range = c(10,2000)), levels = 5)

# tune_res3 <- tune_grid(
#    reg_rf_wf,
#    resamples = data_folds,
#    grid = param_grid,
#    metrics = metric_set(rmse, rsq, mae)
# )

#class_rf_final <- finalize_workflow(class_rf_wf, best_complexity)

#reg_rf_fit2 <- fit(reg_rf_wf, data = data_train)
# 
#save(reg_rf_fit2, file = "reg_rf_fit2.rda")
load(file = "reg_rf_fit2.rda")

augment(reg_rf_fit2, new_data = data_test) %>%
  ggplot(aes(rating_engine_transmission, .pred)) +
  geom_point(alpha = 0.5)

augment(reg_rf_fit2, new_data = data_test) %>%
  rmse(truth = rating_engine_transmission, estimate = .pred)
```

```{r}
# Lab 7

# turns out starting with the later lab was not efficient

# tree_spec <- decision_tree() %>%
#   set_engine("rpart")
# 
# reg_tree_spec <- tree_spec %>%
#   set_mode("regression")
# 
# reg_tree_fit <- reg_tree_spec %>%
#   fit(rating_engine_transmission ~ .-appointment_id, data = data_train)

# class_tree_fit %>%
#   extract_fit_engine() %>%
#   rpart.plot()

# Tried to plot the decision tree but there are too many variables I think.

# augment(reg_tree_fit, new_data = data_test) %>%
#   rmse(truth = rating_engine_transmission, estimate = .pred)
# 
# augment(class_tree_fit, new_data = data_train) %>%
#   ggplot(aes(rating_engine_transmission, .pred)) +
#   geom_abline() +
#   geom_point(alpha = 0.5)
# 
# vip(class_tree_fit)


```

```{r}

# svm_linear_spec <- svm_poly(degree = 1) %>%
#   set_mode("regression") %>%
#   set_engine("kernlab", scaled = FALSE)
# 
# 
# svm_linear_fit <- svm_linear_spec %>% 
#   set_args(cost = 10) %>%
#   fit(rating_engine_transmission ~ ., data = data_train)
# 
# svm_linear_fit

```
